### 2019-01-21 thesis_report/methods.tex
updated thesis

@@

			\begin{figure}[!htb]
			\includegraphics[width=0.95\columnwidth]{images/scattering}
			\caption{Basis for scattering matrix. 
			The `S' region corresponds to the superconductor Hamiltonian without the superconducting term, Eq.~\eqref{eq:ham_smat_superconducting}, `N' to the normal region, Eq.~\eqref{eq:ham_smat_normal}. 
			The coefficients represent the amplitude of the modes present in the system, at a particular energy.
			The different color arrows correspond to the two different spinors in each region.
			For example, $a_{1,L}$ is the amplitude of the rightmoving incoming mode, $\vec{\psi}_1 \exp\left(i k_{1,L} x\right)$}
			\label{fig:scattering}
			\end{figure}

@@

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.75\columnwidth]{images/zigzag_methods.pdf}
		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
		\label{fig:zigzag_methods}}
		\end{figure}

@@

		\comment{We first link the long trajectories to a maximum allowed angle.}
		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$ axis.
		By defining a minimum angle, we thus can filter out the long trajectories.
		We define this angle $\alpha_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
		We suspect that this `grazing' leads to physics which cannot be captured in this simple model, and we thus choose to restrict this method for systems where the chosen trajectory is indeed a good approximation of the longest path.

        We estimate the restriction of the domain for the momentum by defining the angle for the various

        \begin{equation}
        \tan (\alpha) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
        \begin{cases}
        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
        \end{cases}
        \end{equation}

>>>>

\section{Tight binding simulation}

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
	\caption{Figure of the simulated system in Kwant.
	Lattice spacing is made smaller to make the discretization visible.
	The two golden regions are both superconducting, but differ in phase.
	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
	\label{fig:kwant_system}
	\end{figure}

@@

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.75\columnwidth]{images/scattering}
			\caption{Basis for scattering matrix. 
			The `S' region corresponds to the superconductor Hamiltonian without the superconducting term, Eq.~\eqref{eq:ham_smat_superconducting}, `N' to the normal region, Eq.~\eqref{eq:ham_smat_normal}. 
			The coefficients represent the amplitude of the modes present in the system, at a particular energy.
			The different color arrows correspond to the two different spinors in each region.
			For example, $a_{1,L}$ is the amplitude of the rightmoving incoming mode, $\vec{\psi}_1 \exp\left(i k_{1,L} x\right)$}
			\label{fig:scattering}
			\end{figure}

@@

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.75\columnwidth]{images/zigzag_methods.pdf}
		\caption{Schematic of the system, along with relevant dimensions, and the quasiclassical approach.
		The $x^\prime, y^\prime$ axis depicts the rotated frame for the quasiclassical estimate.
		The white trajectory indicates the estimate taken for the longest trajectory allowed by a zigzag.
		\label{fig:zigzag_methods}}
		\end{figure}

@@

		\comment{We first link the long trajectories to a maximum allowed angle.}
		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$ axis.
		By defining a minimum angle, we thus can filter out the long trajectories.
		We define this angle $\beta\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
		We suspect that this `grazing' leads to physics which cannot be captured in this simple model, and we thus choose to restrict this method for systems where the chosen trajectory is indeed a good approximation of the longest path.

        We identify the momentum with its angle by defining it through the reciprocal of the component velocities, given by Eq.~\eqref{eq:methods_angle_of_state}. Note that $k_1$ and $k_2$ are the momenta as defined in Eq.~\eqref{eq:momenta_short_junction}.

        \begin{equation}
        \tan (\beta) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
        \begin{cases}
        \frac{\hbar ^2 k_1}{\frac{\alpha  \meff \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
        \frac{\hbar ^2 k_2}{\frac{\alpha  \meff \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
        \end{cases}
        \label{eq:methods_angle_of_state}
        \end{equation}

        We estimate the restriction of the domain for the momentum by geometrically calculating the minimum angle, as depicted in Fig.\ref{fig:zigzag_methods}. The result:

        \begin{align}
        	\tan \left(\beta_\text{min} \right) = \frac{W}{\sqrt{D^2 - W^2}} \label{eq:beta_min}\\
        	D = \sqrt{z_x^2 + \left(z_y + W \sqrt{1 + \left(\frac{z_y}{z_x}\right)^2}\right)^2} \nonumber
        \end{align}

        The condition for the restricted momentum becomes:
        \begin{equation}
        	\tan \left(\beta\right) \geq \tan \left(\beta_\text{min}\right)
        	\label{eq:restriction_momentum}
        \end{equation}
